paper

### 2024-09-18 paper.qmd
.

```{r results = "hide" , message = FALSE, warning = FALSE}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case0")
print(UPS1.Case0)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- "Conc."
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc."  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case0.LimROTS.rds")
```

@@

trace(LimROTS::testStatistic_with_covariates_Fit, edit = T)
trace(LimROTS::testStatistic_with_covariates_permutating, edit = T)
trace(LimROTS::testStatistic_with_covariates, edit = T)

@@

>>>>

```{r results = "hide" , message = FALSE, warning = FALSE}
# Load necessary packages
library(LimROTS)
library(parallel)
# Load the dataset
data("UPS1.Case0")
print(UPS1.Case0)
# Set random seed for reproducibility
set.seed(1234, kind = "default")
# Set metadata and formula for LimROTS analysis
meta.info <- "Conc."
B <- 1000  # Number of bootstrap samples
K <- dim(UPS1.Case0)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "Conc."
formula.str <- "~ 0 + Conc."  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

trace(LimROTS, edit = T)

limrots.result <- LimROTS(data.exp = UPS1.Case0, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
saveRDS(limrots.result, "../LimROTS paper/UPS1.Case0.LimROTS.rds")
```

@@

trace(LimROTS, edit = T)

@@

length(which(limrots.result$FDR < 0.05))

summary(limrots.result$q_values)
plot(limrots.result$q_values)
hist(limrots.result$q_values)
p.value = limrots.result$pvalue
hist(p.value)

library(qvalue)
q <- qvalue(p.value, pi0.method = "bootstrap", lambda  = seq(0.01, 0.95, 0.01))
plot(q)
hist(q)
summary(q)

pi0est(p.value, pi0.method = "bootstrap")

load("../LimROTS paper/metabolomics/BM21.Case1.rda")

print("BM21.Case1")
data <- assay(BM21.Case1)
formula.str <- "~ 0 + mixing.ratio"
meta.info <- data.frame(colData(BM21.Case1), check.names = FALSE, row.names = row.names(colData(BM21.Case1)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("mixing.ratio1-mixing.ratio2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=T, robust=T)
limma.result <- topTable(fit.ebayes, coef="mixing.ratio1-mixing.ratio2" , number = "Inf")
